---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MOreg)
```

Introduction
MOreg is an R package for fitting linear regression models.

Installation
You can install the development version from GitHub:
```{r}
#devtools::install_github('MaryOwusuBonsu/MOreg')
```

Usage Example
Here is a basic example to show how the MOreg package can be used to fit a linear regression model:

```{r}
# Load MOreg if it is already installed
if (!requireNamespace("MOreg", quietly = TRUE)) {
  stop("MOreg package is not installed. Please install MOreg before proceeding.")
} else {
  library(MOreg)
}

# Sample data
Y <- c(2.5, 6.8, 8.7, 9)
X <- c(15, 25, 30, 29)

# Fit linear model using MOreg
model <- MOreg(Y, X)
print(model)
```

Data
Let's start with a sample data set:

```{r}
Y <- c(2.5, 6.8, 8.7, 9)
X <- c(15, 25, 30, 29)

```

Fitting the Model
We use the MOreg function to fit a linear regression model:

```{r}
model <- MOreg(Y, X)

```

Model Output
The model produces the following output:

beta: Estimated regression coefficients
residuals: Differences between observed and fitted values
sigma_sq_hat: Estimated variance of the residuals
std_err: Standard errors of the regression coefficients
tval: t-values for the regression coefficients
pval: p-values for the regression coefficients
Let's print the results:

```{r}
print(model)
```

Comparison with lm
Let's compare the results from MOreg with those from the lm function in base R:

```{r}
# Using lm
data <- data.frame(Y = Y, X = X)
model_lm <- lm(Y ~ X, data = data)
summary(model_lm)
```


Efficiency Comparison
In addition to correctness, we also assess the efficiency of the MOreg function compared to the base R function lm(). This is done using the bench::mark() function to compare their execution times:
```{r}

# Benchmark MOreg vs lm
benchmark <- bench::mark(
  MOreg(Y, X),
  lm(Y ~ X, data = data),
  check = FALSE
)

# Display benchmark results
benchmark

```

Benchmark Results

We compared the execution times of the `MOreg` function and the `lm()` function using the `bench::mark()` function. The results indicate that `MOreg` is faster than `lm()` for this small dataset:

- **MOreg**: The execution time was 43.3 microseconds (min) and 60.3 microseconds (median), with approximately 14,254 iterations per second.
- **lm()**: The execution time was 306.4 microseconds (min) and 335.7 microseconds (median), with approximately 2,505 iterations per second.

Overall, **MOreg** is about 5 to 6 times faster than `lm()` for this particular example, demonstrating its efficiency for fitting linear regression models.
```

###Conclusion
.MOreg provides a custom implementation of linear regression.
.We have verified its correctness by comparing the results with those from the lm() function.
.Additionally, we have benchmarked its performance, finding its execution time relative to lm().

These tests confirm that MOreg is both correct and efficient for fitting linear regression models.

